\chapter{Conclusions}\label{conclusion}
To understand human motion behaviour for better decision making, many studies have been conducted based on location data collection. Wi-Fi tracking technology is increasingly used due its cost effectiveness and ability to track people at a large scale. For this study, we used the eduroam network of the TU Delft Campus to identify movement patterns. Firstly, states are extracted from the raw Wi-Fi logs.  Subsequently, the event of going from one state to another can be detected as movement. Finally, by counting the number of movement for an observation period, movement patterns can be identified. This project tried to illustrate to what extend movement patterns in and between buildings can be identified from large scale Wi-Fi based location data of the eduroam network. In order to answer this question, there are three applied sub questions:
\begin{itemize}
\item What patterns can be identified moving from and to the TU Delft campus?
\item What movement patterns can be identified between buildings on TU Delft campus?
\item What movement patterns can be identified between large indoor regions of the Faculty of Architecture and the built environment?
\end{itemize}
First of all it can be concluded from the results, that the Wi-Fi network data is to some extent suitable for retrieving movement patterns of people. Expected patterns such as a movement peak between buildings during lunch time, and a morning and afternoon peak of people entering and leaving the campus can be clearly distinguished in the data. Additionally, the data shows actually high movement peaks just before the lectures start. More specific patterns between particular buildings and/or during certain time intervals can easily be derived due to the automated workflow.
\\\\
At building level, the rhythm of the campus is illustrated by time profiles showing the amount of movement for different observation periods. Peaks of high movement could be distinguished just before a lecture starts (at times 8:45, 10:45, 13:45 and 15:45). Additionally, aggregated movement on the map show the expected result that Aula-Library is the most frequently travelled path.
\\\\
Moreover, the indoor movement analysis shows that users of the Faculty of Archicture and the built environment deviate from the trend. This could be explained by the open form of education, because designing in a studio is not limited to strict lecture times. Additionally, the the faculty is also functioning as a meeting place for project groups. An indoor network graph was created of the underlying building floor plan. This successfully illustrates the occupied space for movement. However, the range of APs can extent between building-parts and floors and limits the accuracy of the analysis.